Gaussian Process regression for astronomical time-series

### 2022-09-07 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure}[ht]
  \centering
  \script{GPR_PGM.ipynb}
  \includegraphics[width=\linewidth]{figures/GPR_PGM.pdf}
  \caption{Probabilistic Graphical Model (PGM) got GP regression (adapted from Figure 2.3 of \citealt{} }
  \label{fig:GPR_PGM}
\end{figure}

@@

\begin{figure}[ht]
  \includegraphics[width=3in]{figures/RV_framework.pdf}
  \caption{Schematic of the GP framework of \citet{2015MNRAS.452.2269R} for modelling activity signals in RV data \suz{Figure will be updated with nicer version.}}
  \label{fig:RV_framework}
\end{figure}

>>>>

\begin{figure}[ht]
  \centering
  \script{GPR_PGM.ipynb}
  \includegraphics[width=\linewidth]{figures/GPR_PGM.pdf}
  \caption{Probabilistic Graphical Model (PGM) got GP regression (adapted from Figure 2.3 of \citealt{RW07}). The top layer shows the (known) inputs $\{t\}$}
  \label{fig:GPR_PGM}
\end{figure}

@@

\begin{figure}[ht]
  \includegraphics[width=3in]{static/RV_framework.pdf}
  \caption{Schematic of the GP framework of \citet{2015MNRAS.452.2269R} for modelling activity signals in RV data \suz{Figure will be updated with nicer version.}}
  \label{fig:RV_framework}
\end{figure}
